---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jodudr

<!-- badges: start -->
<!-- badges: end -->

The goal of `jodudr` is to collect functions I've found useful for data analysis.

## Installation

You can install the development version of jodudr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JoDudding/jodudr")
```
Let's load it and some other useful packages

```{r load-jodudr, message=FALSE}
library(jodudr)
library(tidyverse)
library(scales)
```

# Options

## `jo_options()`

This will set the options I use most often. Namely:

- `dplyr.width = Inf`
- `papersize = "a4"`
- `tab.width = 2`
- `width = 80`
- `max.print = 25`
- `stringsAsFactors = FALSE`
- `lubridate.week.start = 6`
- `tibble.print_max = 25`
- `tibble.print_min = 25`
- `tibble.width = Inf`
- `dplyr.summarise.inform = FALSE`
- `tidyverse.quiet = TRUE`

# Date functions

## `eom_date()`

This determines the last day of month n months ago:

```{r eom-date-example-1}
eom_date(ymd('2022-04-19'), 13)
```

Used without parameters it will give the last day of the current month (run on 
`r lubridate::today()`):
```{r eom-date-example-2}
eom_date()
```

## `friday_wk()`

Get last day of the week where week ends on Friday

```{r friday-wk-example-1}
d <- ymd('2024-02-06') # a tuesday
friday_wk(d)
```

# Theming

## `jo_pal_grad()`

This will create a vector of n colours from my primary colour to my secondary colour.

```{r jo-pal-grad-example-1}
jo_pal_grad(6) |> 
  show_col()
```

## `theme_jo()`

Apply my theme to ggplot2 charts.

```{r theme_jo-example-1}
ggplot(mapping = aes(x = letters[1:10], y = 1:10, fill = rep(c('o', 'e'), times = 5))) +
  geom_col() +
  labs(x = 'letter', y = 'number', fill = 'odd/even', title = 'dummy chart') +
  theme_jo()
```

# Analysis helpers

## `summaryx()`

```{r summaryx-example-1}
as_tibble(mtcars) |> 
  summaryx(mpg) |> 
  glimpse()
```
Will also work with grouping applied.

```{r summaryx-example-2}
dplyr::as_tibble(mtcars) |> 
  group_by(cyl) |> 
  summaryx(mpg) |> 
  select(cyl, min, max, mean)
```

